Weighted Model Counting Without Parameter Variables

### 2021-06-14 doc/SAT_long_talk/talk.tex
Some TikZ

\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage{tikz}
\usepackage{listings}
\usepackage{complexity}
\usepackage{mathtools}
\usepackage{booktabs}

@@

\usetikzlibrary{arrows}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{shapes}

@@

% ~15 slides
% Section: Motivation
% * the problem of computing probability,
% * WMC (perhaps with a bigger example of a BN encoding, to emphasise the clutter)
% Section: An Alternative Formulation
% * Definition of WMC and MC-WMC
% * Pseudo-Boolean functions, my notation, PBP instance
% Section: Correctness
% Section: Experimental Results
% * Cactus plot
% * Scatter plots
% * Box plots
% * Summary

@@

@@

\section{An Alternative Formulation}

@@

\begin{frame}{From WMC to PBP}
  The WMC instance has \structure{$x$} as the only \alert{indicator} variable
  and \structure{$p$}, \structure{$q$} as \alert{parameter} variables with
  weights \structure{$w(p) = 0.2$}, \structure{$w(q) = 0.8$}, and
  \structure{$w(\neg p) = w(\neg q) = 1$}.
  \begin{center}
    \begin{tabular}{llll}
      \toprule
      WMC Clause & \onslide<2->{In CNF} & \onslide<3->{Pseudo-Boolean Function} & \\
      \midrule
      $\neg x \Rightarrow p$ & \onslide<2->{$x \lor p$} & \onslide<3->{$[\neg x]_1^{0.2}$} & \\
      $p \Rightarrow \neg x$ & \onslide<2->{$\neg x \lor \neg p$} & & \onslide<4->{$[x]^{0.8}_{0.2}$} \\
      $x \Rightarrow q$ & \onslide<2->{$\neg x \lor q$} & \onslide<3->{$[x]_1^{0.8}$} & \\
      $q \Rightarrow x$ & \onslide<2->{$x \lor \neg q$} & & \\
      $\neg x$ & \onslide<2->{$\neg x$} & \onslide<3->{$[\neg x]_0^1$} & \onslide<4->{$[\neg x]_0^1$} \\
      \bottomrule
    \end{tabular}
  \end{center}
\end{frame}

@@

\begin{frame}{Experimental Results}
  \centering
  \input{cumulative}
\end{frame}

\begin{frame}{Experimental Results}
  \centering
  \input{scatter1}
\end{frame}

\begin{frame}{Experimental Results}
  \centering
  \input{scatter2}
\end{frame}

>>>>

\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage{tikz}
\usepackage{listings}
\usepackage{complexity}
\usepackage{mathtools}
\usepackage{booktabs}
\usepackage{xcolor}

@@

\usetikzlibrary{arrows}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{shapes}
\usetikzlibrary{positioning}
\usetikzlibrary{tikzmark}
\usetikzmarklibrary{listings}

\tikzstyle{every picture}+=[remember picture]

\newcounter{tmkcount}
\tikzset{
  use tikzmark/.style={
    remember picture,
    overlay,
    execute at end picture={
      \stepcounter{tmkcount}
    },
  },
  tikzmark suffix={-\thetmkcount}
}

\definecolor{color1}{HTML}{1b9e77}
\def\speciallstcolor{\begingroup\color{color1}}
\def\endspeciallstcolor{\endgroup}

\definecolor{color2}{HTML}{d95f02}
\def\speciallstcolortwo{\begingroup\color{color2}}
\def\endspeciallstcolortwo{\endgroup}

\definecolor{color3}{HTML}{7570b3}
\def\speciallstcolorthree{\begingroup\color{color3}}
\def\endspeciallstcolorthree{\endgroup}

\definecolor{color4}{HTML}{e7298a}
\def\speciallstcolorfour{\begingroup\color{color4}}
\def\endspeciallstcolorfour{\endgroup}

\definecolor{color5}{HTML}{66a61e}
\def\speciallstcolorfive{\begingroup\color{color5}}
\def\endspeciallstcolorfive{\endgroup}

\definecolor{color6}{HTML}{e6ab02}
\def\speciallstcolorsix{\begingroup\color{color6}}
\def\endspeciallstcolorsix{\endgroup}

\definecolor{color7}{HTML}{a6761d}
\def\speciallstcolorseven{\begingroup\color{color7}}
\def\endspeciallstcolorseven{\endgroup}

@@

@@

\begin{frame}[fragile]{The Problem with Assigning Weights to Literals}
  \begin{columns}[t]
    \begin{column}{0.5\textwidth}
      \begin{block}{A Simple Bayesian Network}
        \centering
        \begin{tikzpicture}[edge from parent/.style={draw,-{Latex}}]
          \node[draw,circle] at (0, 0) (a) {$A$}
          child {node[draw,circle] (b) {$B$}};
        \end{tikzpicture}
      \end{block}
      \begin{itemize}
      \item from \structure{2 binary} variables
      \item to \structure{8} variables and \structure{17} clauses
      \item with lots of redundancy
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{block}{Its WMC Encoding}
        \vspace{-0.2cm}
\begin{lstlisting}[basicstyle=\scriptsize,escapeinside={(*}{*)},name=codeL]
p cnf 8 17
(*\only<2->{\aftergroup\speciallstcolor}*)-2 -1 0(*\only<2->{\aftergroup\endspeciallstcolor}*)
(*\only<2->{\aftergroup\speciallstcolor}*)1 2 0(*\only<2->{\aftergroup\endspeciallstcolor}*)
(*\only<2->{\aftergroup\speciallstcolortwo}*)-3 1 0(*\only<2->{\aftergroup\endspeciallstcolortwo}*)
(*\only<2->{\aftergroup\speciallstcolortwo}*)-1 3 0(*\only<2->{\aftergroup\endspeciallstcolortwo}*)
(*\only<2->{\aftergroup\speciallstcolorthree}*)-5 -1 0(*\only<2->{\aftergroup\endspeciallstcolorthree}*)
(*\only<2->{\aftergroup\speciallstcolorthree}*)-5 -4 0(*\only<2->{\aftergroup\endspeciallstcolorthree}*)
(*\only<2->{\aftergroup\speciallstcolorthree}*)1 4 5 0(*\only<2->{\aftergroup\endspeciallstcolorthree}*)
(*\only<2->{\aftergroup\speciallstcolorfour}*)-6 -1 0(*\only<2->{\aftergroup\endspeciallstcolorfour}*)
(*\only<2->{\aftergroup\speciallstcolorfour}*)-6 4 0(*\only<2->{\aftergroup\endspeciallstcolorfour}*)
(*\only<2->{\aftergroup\speciallstcolorfour}*)-4 1 6 0(*\only<2->{\aftergroup\endspeciallstcolorfour}*)
(*\only<2->{\aftergroup\speciallstcolorfive}*)-7 1 0(*\only<2->{\aftergroup\endspeciallstcolorfive}*)
(*\only<2->{\aftergroup\speciallstcolorfive}*)-7 -4 0(*\only<2->{\aftergroup\endspeciallstcolorfive}*)
(*\only<2->{\aftergroup\speciallstcolorfive}*)-1 4 7 0(*\only<2->{\aftergroup\endspeciallstcolorfive}*)
(*\only<2->{\aftergroup\speciallstcolorsix}*)-8 1 0(*\only<2->{\aftergroup\endspeciallstcolorsix}*)
(*\only<2->{\aftergroup\speciallstcolorsix}*)-8 4 0(*\only<2->{\aftergroup\endspeciallstcolorsix}*)
(*\only<2->{\aftergroup\speciallstcolorsix}*)-4 -1 8 0(*\only<2->{\aftergroup\endspeciallstcolorsix}*)
(*\only<2->{\aftergroup\speciallstcolorseven}*)-4 0(*\only<2->{\aftergroup\endspeciallstcolorseven}*)
c weights 1.0 1.0 0.5 1.0 \
0.5 1.0 1.0 1.0 0.6 1.0 \
0.4 1.0 0.1 1.0 0.9 1.0
\end{lstlisting}
        \vspace{-0.2cm}
      \end{block}
    \end{column}
  \end{columns}
  \only<2->{
    \begin{tikzpicture}[overlay,use tikzmark]
      \node[above right = 0 and 15 mm of pic cs:line-codeL-3-end] {\color{color1}{$\neg x_1 \Leftrightarrow x_2$}};
      \node[above right = 0 and 15 mm of pic cs:line-codeL-5-end] {\color{color2}{$x_1 \Leftrightarrow x_3$}};
      \node[above right = 0.5 ex and 10 mm of pic cs:line-codeL-8-end] {\color{color3}{$\neg x_1 \land \neg x_4 \Leftrightarrow x_5$}};
      \node[above right = 0.5 ex and 10 mm of pic cs:line-codeL-11-end] {\color{color4}{$\neg x_1 \land x_4 \Leftrightarrow x_6$}};
      \node[above right = 0.5 ex and 10 mm of pic cs:line-codeL-14-end] {\color{color5}{$x_1 \land \neg x_4 \Leftrightarrow x_7$}};
      \node[above right = 0.5 ex and 10 mm of pic cs:line-codeL-17-end] {\color{color6}{$x_1 \land x_4 \Leftrightarrow x_8$}};
      \node[above right = -0.5 ex and 20 mm of pic cs:line-codeL-18-end] {\color{color7}{$\neg x_4$}};
    \end{tikzpicture}
  }
\end{frame}

@@

\section{An Alternative Formulation}
% TODO: Definition of WMC and MC-WMC

@@

\begin{frame}{From WMC to PBP}
  \begin{example}
    \begin{itemize}
    \item Indicator variable: \structure{$x$}
    \item Parameter variables: \structure{$p$}, \structure{$q$}
    \item Weights: \structure{$w(p) = 0.2$}, \structure{$w(q) = 0.8$}, and \structure{$w(\neg p) = w(\neg q) = 1$}
    \end{itemize}
    \begin{center}
      \begin{tabular}{llll}
        \toprule
        WMC Clause & \onslide<2->{In CNF} & \onslide<3->{Pseudo-Boolean Function} & \\
        \midrule
        $\neg x \Rightarrow p$ & \onslide<2->{$x \lor p$} & \onslide<3->{$[\neg x]_1^{0.2}$} & \\
        $p \Rightarrow \neg x$ & \onslide<2->{$\neg x \lor \neg p$} & & \onslide<4->{$[x]^{0.8}_{0.2}$} \\
        $x \Rightarrow q$ & \onslide<2->{$\neg x \lor q$} & \onslide<3->{$[x]_1^{0.8}$} & \\
        $q \Rightarrow x$ & \onslide<2->{$x \lor \neg q$} & & \\
        $\neg x$ & \onslide<2->{$\neg x$} & \onslide<3->{$[\neg x]_0^1$} & \onslide<4->{$[\neg x]_0^1$} \\
        \bottomrule
      \end{tabular}
    \end{center}
  \end{example}
\end{frame}

@@

\begin{frame}{Experimental Results}
  \centering
  \includegraphics[width=\textwidth]{cumulative}
\end{frame}

\begin{frame}{Experimental Results}
  \centering
  \includegraphics[width=\textwidth]{scatter1}
\end{frame}

\begin{frame}{Experimental Results}
  \centering
  \includegraphics[width=\textwidth]{scatter2}
\end{frame}

\begin{frame}{Experimental Results}
  \centering
  \includegraphics[width=\textwidth]{box}
\end{frame}
% TODO: fit the plot to the left half of the slide, add observations on the
% right
